Meta-analysis

### 2019-07-22 05_MetaAnalysis.Rmd
updating explainations and comments

The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in

```{r LSD_2_MSE}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
colnames(PM_MB_means)

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

```
![calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

@@

>>>>

The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221). Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/). A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.

```{r LSD_2_MSE}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
#  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

```
![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

@@

Now for the trickier part creating 'Sampling Variance from NAs.
```{r}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == NA)%>%
   select(Trial_ref)%>%
   distinct()
```
